---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# widgetdown

[![Travis build status](https://travis-ci.org/jayhesselberth/widgetdown.svg?branch=master)](https://travis-ci.org/jayhesselberth/widgetdown)

The goal of widgetdown is to test the use of htmlwidgets in a pkgdown website, without bloating the [pkgdown](https://github.com/r-lib/pkgdown) package itself.

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jayhesselberth/widgetdown")
```
## Widgets in pkgdown sections

```{r, echo=FALSE}
# set seed for reproducible widget id
if (requireNamespace("htmltools", quietly = TRUE)) {
  htmlwidgets::setWidgetIdSeed(42)
}
```

The package tests the use of htmlwidgets in pkgdown:

* [Home page](https://jayhesselberth.github.io/widgetdown/index.html) (i.e., `README.Rmd` or `index.Rmd`)
* [Reference topics](https://jayhesselberth.github.io/widgetdown/reference/test-widgets.html) using Rd `@examples`.
* [Vignettes](https://jayhesselberth.github.io/widgetdown/articles/widgetdown.html)

widgetdown tests several widgets [available from RStudio](https://www.htmlwidgets.org/showcase_leaflet.html).

### leaflet

```{r leaflet}
library(leaflet)
  leaflet() %>%
  addTiles() %>%
  addMarkers(
  lng=174.768,
  lat=-36.852,
  popup="The birthplace of R"
)
```

### heatmaply

```{r heatmaply}
library(heatmaply)
heatmaply(mtcars, k_row = 3, k_col = 2)
```

### plotly

```{r plotly}
library(plotly)
plot_ly(midwest,
  x = ~percollege,
  color = ~state,
  type = "box"
)
```

### DiagrammeR

```{r diagrammer}
library(DiagrammeR)
grViz("
  digraph {
    layout = twopi
    node [shape = circle]
    A -> {B C D} 
  }")
```

### Dygraphs

```{r dygraphs}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

### networkD3

```{r networkd3, message=FALSE}
library(networkD3)
data(MisLinks, MisNodes)
forceNetwork(Links = MisLinks, Nodes = MisNodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.4)

```

### rbokeh

```{r rbokeh, warning=FALSE}
library(rbokeh)
figure() %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
    color = Species, glyph = Species,
    hover = list(Sepal.Length, Sepal.Width))
```

### highcharter

```{r highcharter}
library(magrittr)
library(highcharter)
highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_series_scatter(mtcars$wt, mtcars$mpg,
                        mtcars$drat, mtcars$hp)
```
