---
title: "Debugging DT"
author: "Jay Hesselberth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{datatables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Tables with `DT::datatable()` are not rendering correctly in pkgdown.

* The table from the top example renders OK as an Rmarkdown > HTML, so I'm thinking that the issue has something to do with the container layout used in pkgdown.

Here's a bunch of different things I've tried.

## DT

Currently DT tables fill the entire container, but the internal columns do not.

```{r dt}
library(DT)
datatable(iris)
```

## DT - filter

Adding `filter` fixes the column width issue. Would be nice if columns widths were fixed without this.

Issue filed at https://github.com/rstudio/DT/issues/563.

Hint from from https://saurfang.github.io/pkgdown.example/reference/datatable.html

```{r dt_filter}
datatable(iris, filter = 'top')
```
